Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-10-22 paper/paperv3.qmd
changing from effect size back to coefficient

```{r}
# Are hypotheses supported by the model? note to future readers...this part could have been done way easier, and you will have to trust our process that this was the path of least resistence for us at the point of final revisions!
# extract_p <- function(h, tails = 1) {
#   if (tails == 1) {
#     map_dbl(mod_sens, \(m) pnorm(m[[h]]["age10:age_catOld", "z value"]))
#   } else if (tails == 2) {
#     map_dbl(mod_sens, \(m) 2 * pnorm(m[[h]]["age10:age_catOld", "z value"],
#                                      lower.tail = (m[[h]]["age10:age_catOld", "z value"] < 0)
#                                      ))
#   } else {
#     stop("tails must be 1 or 2")
#   }
# }
extract_p <- function(h) {
  map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Pr(>|z|)"])
}
extract_aic <- function(h) {
  map_dbl(mod_sens, paste(h, "aic", sep = "_"))
}
aic_weight <- function(x) {
  rellik <- exp(-0.5 * (x - min(x)))
  rellik / sum(rellik)
}
extract_coef <- function(h) {
  #map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Estimate"])
  exp(map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Estimate"]))
}
extract_se <- function(h) {
  map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Std. Error"])
}

@@

left_join(
  pivot_longer(p_tbl, -age_cutoff, names_to = "hypothesis", values_to = "p"),
  pivot_longer(coef_tbl, -age_cutoff, names_to = "hypothesis", values_to = "coef"),
  by = c("age_cutoff", "hypothesis")
  ) %>% 
  left_join(
    pivot_longer(se_tbl, -age_cutoff, names_to = "hypothesis", values_to = "se"),
    by = c("age_cutoff", "hypothesis")
  ) %>% 
  ggplot(aes(age_cutoff, coef)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_pointrange(aes(size = p, 
                      color = p < 0.05, 
                      ymin = coef - 1.96 * se,
                      ymax = coef + 1.96 * se)) +
  labs(x = "Senescence onset (years)", 
       y = "Effect size") +
  scale_size_continuous(range = c(0.25, 1)) +
  expand_limits(y = 3) +
  facet_wrap(~hypothesis) +
  theme(legend.position = "none")

>>>>

```{r}
# Are hypotheses supported by the model? note to future readers...this part could have been done way easier, and you will have to trust our process that this was the path of least resistence for us at the point of final revisions!
# extract_p <- function(h, tails = 1) {
#   if (tails == 1) {
#     map_dbl(mod_sens, \(m) pnorm(m[[h]]["age10:age_catOld", "z value"]))
#   } else if (tails == 2) {
#     map_dbl(mod_sens, \(m) 2 * pnorm(m[[h]]["age10:age_catOld", "z value"],
#                                      lower.tail = (m[[h]]["age10:age_catOld", "z value"] < 0)
#                                      ))
#   } else {
#     stop("tails must be 1 or 2")
#   }
# }
extract_p <- function(h) {
  map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Pr(>|z|)"])
}
extract_aic <- function(h) {
  map_dbl(mod_sens, paste(h, "aic", sep = "_"))
}
aic_weight <- function(x) {
  rellik <- exp(-0.5 * (x - min(x)))
  rellik / sum(rellik)
}
extract_coef <- function(h) {
  map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Estimate"])
}
extract_se <- function(h) {
  map_dbl(mod_sens, \(m) m[[h]]["age10:age_catOld", "Std. Error"])
}

@@

left_join(
  pivot_longer(p_tbl, -age_cutoff, names_to = "hypothesis", values_to = "p"),
  pivot_longer(coef_tbl, -age_cutoff, names_to = "hypothesis", values_to = "coef"),
  by = c("age_cutoff", "hypothesis")
  ) %>% 
  left_join(
    pivot_longer(se_tbl, -age_cutoff, names_to = "hypothesis", values_to = "se"),
    by = c("age_cutoff", "hypothesis")
  ) %>% 
  ggplot(aes(age_cutoff, coef)) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_pointrange(aes(size = p, 
                      color = p < 0.05, 
                      ymin = coef - 1.96 * se,
                      ymax = coef + 1.96 * se)) +
  labs(x = "Senescence onset (years)", 
       y = "Coefficient") +
  scale_size_continuous(range = c(0.25, 1)) +
  expand_limits(y = 3) +
  facet_wrap(~hypothesis) +
  theme(legend.position = "none")
